The Astropy Project

### 2017-11-20 main.tex
moved a number of comments to issues

\subsubsection{Single Model Definition and Evaluation}
\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}
Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}. A model is instantiated by passing in values (scalars or arrays) for its parameters. A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints. The value and constraints can be updated by assignment. Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values. Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials). Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules. A model is evaluated by calling it as a function.

@@

\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}

@@

\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}

>>>>

\subsubsection{Single Model Definition and Evaluation}

%\inlinecomment{hamogu: I tihnk this is too techical. I know it's a complex subpackage but I had trouble understanding this section even as a regular user.}

Most models are defined by parameters and maintain an ordered list of parameter names, \texttt{Model.param\_names}. A model is instantiated by passing in values (scalars or arrays) for its parameters. A parameter is a descriptor that provides a proxy for the value and stores additional information -- default value, default unit, and parameter constraints. The value and constraints can be updated by assignment. Supported parameter constraints include \texttt{fixed}, and \texttt{tied} parameters, and \texttt{bounds} on parameter values. Most models have a fixed parameter set but for some (e.g., polynomials), the number of parameters is defined by another argument (e.g., degree-of-freedom in the case of polynomials). Parameters support arithmetic operations and are combined with the inputs during evaluation using the \package{numpy} broadcasting rules. A model is evaluated by calling it as a function.

@@

%\inlinecomment{APW}{Add citations for the different optimizaton algorithms in paragraph above?}

@@

%\inlinecomment{TPR}{We should put the releases of sphinx-automodapi on Zenodo and cite this}
